The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-16 paper/mri_paper.tex
more equations + formatting
formatting appendix
N31 (u)
appendix a
N_22(psi)
full nonlinear appendix
added figure
more endcaps discussion

\section{Conclusions}

\newpage
\begin{appendices}
\begin{widetext}
\section*{Appendix A.}
\begin{multline}
N_{31}^{(A)} = -i Q \left(A_{11}\cdot\partial_x \Psi_{20}\right) - i Q \left(A_{11} \cdot \partial_x \Psi_{20}^*\right)
 + i Q \left(A_{11}^* \cdot \partial_x \Psi_{22}\right) + i 2 Q \left(\partial_x A_{11}^* \cdot \Psi_{22}\right) \\
 + i Q \left(\Psi_{11} \cdot \partial_x A_{20}\right) + i Q \left(\Psi_{11} \cdot \partial_x A_{20}^*\right) - i Q \left(\Psi_{11}^* \cdot \partial_x A_{22} \right) - i 2 Q \left(\partial_x \Psi_{11}^* \cdot A_{22}\right)
\end{multline}

@@

>>>>

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.5]{twoorders_Bfield.eps}
\caption{First order (left) and second order (right) velocity perturbations. Streamlines represent velocity in the vertical-radial plane, where thicker streamlines correspond to faster speeds. The colorbar represents azimuthal velocity.}
\end{figure*}

\section{Discussion}

Our domain is designed to be relevant to the design of the Princeton Plasma Physics Laboratory (PPPL) MRI experiment (\citei{Ji:2001kd}). A challenge for all MRI experiments is to reduce all extraneous flows which may stabilize the MRI or obscure its detection. In particular, care must be taken to mitigate meridional flows introduced by the endcaps of the experimental apparatus. The PPPL MRI experiment employs a novel design using concentric, differentially rotating rings as endcaps (\citei{Schartman:2009df}). In this investigation, we use periodic vertical boundary conditions, so our set-up represents an idealized domain where endcap contamination does not exist. Future work will address specifically our predictions for the PPPL MRI experiment.

\newpage
\begin{appendices}
\begin{widetext}
\section*{Appendix A.}

Second order nonlinear terms: \\

\beq
\begin{split}
N_{22}^{(\Psi)} = & \, i Q \Psi_{11} \cdot \left(\partial_x^3 \Psi_{11} - Q^2 \partial_x \Psi_{11}\right) - \partial_x \Psi_{11} \cdot \left(i Q \partial_x^2 \Psi_{11} - i Q^3 \Psi_{11}\right) \\
& + \frac{2}{\beta}\partial_x A_{11} \cdot \left(i Q \partial_x^2 A_{11} - i Q^3 A_{11}\right) - \frac{2}{\beta} i Q A_{11} \cdot \left(\partial_x^3 A_{11} - Q^2 \partial_x A_{11}\right)
\end{split}
\eeq

\beq
\begin{split}
N_{22}^{(u)} = & \, i Q \Psi_{11} \cdot \partial_x u_{11} - \partial_x \Psi_{11} \cdot i Q u_{11} - \frac{2}{\beta} i Q A_{11} \cdot \partial_x B_{11} + \frac{2}{\beta} \partial_x A_{11} \cdot i Q B_{11}
\end{split}
\eeq

\beq
N_{22}^{(A)} = - i Q A_{11} \cdot \partial_x \Psi_{11} + \partial_x A_{11} \cdot i Q \Psi_{11}
\eeq

\beq
N_{22}^{(B)} = i Q \Psi_{11} \cdot \partial_x B_{11} - \partial_x \Psi_{11} \cdot i Q B_{11} - i Q A_{11} \cdot \partial_x u_{11} + \partial_x A_{11} \cdot i Q u_{11}
\eeq

\beq
\begin{split}
N_{20}^{(\Psi)} = & \, i Q \Psi_{11} \cdot \left(\partial_x^3 \Psi_{11}^* - Q^2 \partial_x \Psi_{11}^*\right) - \partial_x \Psi_{11} \cdot \left(i Q \partial_x^2 \Psi_{11}^* - i Q^3 \Psi_{11}^*\right) \\
& \frac{2}{\beta} \partial_x A_{11} \cdot \left(i Q \partial_x^2 A_{11}^* - i Q^3 A_{11}^*\right) - \frac{2}{\beta} i Q A_{11} \cdot \left(\partial_x^3 A_{11}^* - Q^2 \partial_x A_{11}^*\right)
\end{split}
\eeq

\beq
N_{20}^{(u)} = i Q \Psi_{11} \cdot \partial_x u_{11}^* - \partial_x \Psi_{11} \cdot i Q u_{11}^* - \frac{2}{\beta} i Q A_{11} \cdot \partial_x B_{11}^* + \frac{2}{\beta} \partial_x A_{11} \cdot i Q B_{11}^*
\eeq

\beq
N_{20}^{(A)} = - i Q A_{11} \cdot \partial_x \Psi_{11}^* - \partial_x A_{11} \cdot i Q \Psi_{11}^*
\eeq

\beq
N_{20}^{(B)} = i Q \Psi_{11} \cdot \partial_x B_{11}^* - \partial_x \Psi_{11} \cdot i Q B_{11}^* - i Q A_{11} \cdot \partial_x u_{11}^* + \partial_x A_{11} \cdot i Q u_{11}^*
\eeq \\

Third order nonlinear terms: \\

\beq
\begin{split}
N_{31}^{(\Psi)} = &  \, i Q \left(\Psi_{11} \cdot \partial_x^3 \Psi_{20}\right) + i Q \left(\Psi_{11} \cdot \partial_x^3\Psi_{20}^*\right) - i Q \left(\Psi_{11}^* \cdot \partial_x^3 \Psi_{22}\right) - i 2 Q \left(\partial_x \Psi_{11}^* \cdot \partial_x^2 \Psi_{22}\right) \\
& + i 8 Q^3 \left(\partial_x\Psi_{11}^* \cdot \Psi_{22}\right) + i 4 Q^3 \left(\Psi_{11}^* \cdot \partial_x \Psi_{22}\right) + \frac{2}{\beta}\left[ - i Q \left(A_{11} \cdot \partial^3 A_{20}\right) - i Q \left(A_{11} \cdot \partial_x^3 A_{20}^*\right) \right]\\
& + \frac{2}{\beta}\left[i Q \left(A_{11}^* \cdot \partial_x^3 A_{22}\right) + i 2 Q \left(\partial_x A_{11}^* \cdot \partial_x^2 A_{22}\right) - i 8 Q^3 \left(\partial_x A_{11}^* \cdot A_{22}\right) - i 4 Q^3 \left(A_{11}^* \cdot \partial_x A_{22}\right)\right] \\
& + i 2 Q \left(\Psi_{22} \cdot \partial_x^3 \Psi_{11}^*\right) - i 2 Q^3\left(\Psi_{22} \cdot \partial_x \Psi_{11}^* \right) - i Q \left(\partial_x \Psi_{20} \cdot \partial_x^2 \Psi_{11}\right) + i Q \left(\partial_x \Psi_{22} \cdot \partial_x^2 \Psi_{11}^*\right) \\
& - i Q \left(\partial_x \Psi_{20}^* \cdot \partial_x^2 \Psi_{11}\right) + i Q^3 \left(\partial_x \Psi_{20} \cdot \Psi_{11}\right) + i Q^3 \left(\partial_x \Psi_{20}^* \cdot \Psi_{11}\right) - i Q^3 \left(\partial_x \Psi_{22} \cdot \Psi_{11}^*\right) \\
& + \frac{2}{\beta} \left[ - i 2 Q \left(A_{22} \cdot \partial_x^3 A_{11}^*\right) + i 2 Q^3 \left(A_{22} \cdot \partial_x A_{11}^*\right) + i Q \left(\partial_x A_{20} \cdot \partial_x^2 A_{11}\right) - i Q \left(\partial_x A_{22} \cdot \partial_x^2 A_{11}^*\right) \right] \\
& + \frac{2}{\beta} \left[ i Q \left(\partial_x A_{20}^* \cdot \partial_x^2 A_{11}\right) - i Q^3 \left(\partial_x A_{20} \cdot A_{11}\right) - i Q^3 \left(\partial_x A_{20}^* \cdot A_{11}\right) + i Q^3 \left(\partial_x A_{22} \cdot A_{11}^*\right)\right]
\end{split}
\eeq

\beq
\begin{split}
N_{31}^{(u)} = \, & i Q \left(\Psi_{11} \cdot \partial_x u_{20}\right) + i Q \left(\Psi_{11} \cdot \partial_x u_{20}^*\right) - i Q \left(\Psi_{11}^* \cdot \partial_x u_{22}\right) - i 2 Q \left(\partial_x \Psi_{11}^* \cdot u_{22}\right) \\
& - i Q \left(u_{11} \cdot \partial_x \Psi_{20} \right) - i Q \left(u_{11} \cdot \partial_x \Psi_{20}^*\right) + i Q \left(u_{11}^* \cdot \partial_x \Psi_{22} \right) + i 2 Q \left(\partial_x u_{11}^* \cdot \Psi_{22}\right) \\
& +\frac{2}{\beta}\left[- i Q \left(A_{11} \cdot \partial_x B_{20}\right) - i Q \left(A_{11} \cdot \partial_x B_{20}^*\right) + i Q \left(A_{11}^* \cdot \partial_x B_{22}\right) + i 2 Q \left(\partial_x A_{11}^* \cdot B_{22}\right)\right] \\
& +\frac{2}{\beta}\left[ i Q \left(B_{11} \cdot \partial_x A_{20}\right) + i Q \left(B_{11} \cdot \partial_x A_{20}^*\right) - i Q \left(B_{11}^* \cdot \partial_x A_{20}\right) - i 2 Q \left(\partial_x B_{11}^* \cdot A_{22}\right)\right]
\end{split}
\eeq

\beq
\begin{split}
N_{31}^{(A)} =\, & -i Q \left(A_{11}\cdot\partial_x \Psi_{20}\right) - i Q \left(A_{11} \cdot \partial_x \Psi_{20}^*\right)
 + i Q \left(A_{11}^* \cdot \partial_x \Psi_{22}\right) + i 2 Q \left(\partial_x A_{11}^* \cdot \Psi_{22}\right) \\
 & + i Q \left(\Psi_{11} \cdot \partial_x A_{20}\right) + i Q \left(\Psi_{11} \cdot \partial_x A_{20}^*\right) - i Q \left(\Psi_{11}^* \cdot \partial_x A_{22} \right) - i 2 Q \left(\partial_x \Psi_{11}^* \cdot A_{22}\right)
\end{split}
\eeq

\beq
\begin{split}
N_{31}^{(B)} = \, & i Q \left(\Psi_{11} \cdot \partial_x B_{20}\right) + i Q \left(\Psi_{11} \cdot \partial_x B_{20}^*\right) - i Q \left(\Psi_{11}^* \cdot \partial_x B_{22}\right) - i 2 Q\left(\partial_x \Psi_{11}^* \cdot B_{22}\right) \\
& - i Q \left(B_{11} \cdot \partial_x \Psi_{20}\right) - i Q \left(B_{11} \cdot \partial_x \Psi_{20}^*\right) + i Q\left(B_{11}^* \cdot \partial_x \Psi_{22}\right) + i 2 Q \left(\partial_x B_{11}^* \cdot \Psi_{22}\right) \\
& - i Q \left(A_{11} \cdot \partial_x u_{20}\right) - i Q \left(A_{11} \cdot \partial_x u_{20}^*\right) + i Q \left(A_{11}^* \cdot \partial_x u_{22}\right) + i 2 Q \left(\partial_x A_{11}^* \cdot u_{22}\right) \\
& i Q \left(u_{11} \cdot \partial_x A_{20} \right) + i Q \left(u_{11} \cdot \partial_x A_{20}^*\right) - i Q \left(u_{11}^* \cdot \partial_x A_{22}\right) - i 2 Q \left(\partial_x u_{11}^* \cdot A_{22}\right)
\end{split}
\eeq

@@

\bibitem[{Schartman, et al.}]{Schartman:2009df}
Schartman, E, Ji, H, Burin, M J, Rev Sci Instrum, 80, 024501
